\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-15 paper/draft.tex
Fixes

\usepackage{soul}
\usepackage{xspace}
\usepackage{color}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{alltt}
\usepackage{amssymb}
\usepackage{amsmath}

@@

This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top Node.js v8.9.4.
We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses developed with \sys~\sx{impl2}.
We postpone discussion of how other environments diverge from JavaScript for later~\sx{reqs}.

The aforementioned dialysis design can be implemented in either of two ways.
The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place. % with the techniques described earlier.
The second approach is to implement \sys as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.

With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of Node's module system;
  we went with the second approach, as avoiding tight coupling has several benefits:
  it does not require \sys's users to have a second Node copy only for running analyses;
  it removes \sys's developers from the critical path of updates between the Node developers and its users; 
  and it simplifies \sys's comparison with vanilla Node (both in terms of performance and correctness).
The primary drawback was missing a few  opportunities for runtime-performance and development-effort.

% It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.

@@

Node's module system is implemented entirely in JavaScript, exposing a library-local \ttt{require} function for importing modules.
Loading a fresh module with \ttt{require("foo");} corresponds to the following five stages, all of which are augmented by \sys:
(R) Resolution: identify the file to which the module specified corresponds, locate it in the file-system, and assign its absolute path as a module identifier.
(L) Loading: depending on the file type, identify the corresponding loader---\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc
% Identifiers are absolute paths.
(W) Wrapping: wrap the module so local names do not escape the module's scope and Node's module-local names get resolved.
(E) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
(C) Caching: add the module to a handful of module-related caches, for purposes of consistency and performance.

% The resolution algorithm is somewhat convoluted, because it depends on several different facts (including the type of the file requested, whether it is a globally installed, whether it is a directory \etc).
% It does not require any \sys support beyond copying the directory that contains the source code of the all the modules onto the remote host.
\sys interposes on all of these steps to facilitate transformations.
Interposing on resolution (R) makes the module identifier available to \sys without affecting the (incredibly convoluted!) module resolution algorithm.
If the module's type is one \sys can analyze, it fetches the corresponding analysis during loading (L).
Wrapping (W) and evaluation (E) are where \sys transforms the module boundary.
\sys replaces Node's wrapper function in order to add a last variable in the function definition, \ttt{CTX}.
\sys comes with a hard-coded list of names corresponding to the specific version of EcmaScript and Node.js:
  (i) identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit;
  (ii) Node's global names are described at various parts of the documentation; and
  (iii) library-local required close inspection of Node's internals; fortunately, these were only five names.

@@

% \begin{verbatim}
% let lib = `
%  function (exports, require, module,
%            __filename, __dirname, CTX) {
%    let Math = CTX.Math
%    let console = CTX.console
%    //...[more definitions]
%    ${moduleSource}
%  });`;
% \end{verbatim}

We found it useful to add an option for white- and black-listing libraries.
The configuration object accepts \ttt{only} and \ttt{not} expressions that indicate whether a module identifier will be part of the analysis.
These expressions contain sets of sets of regular expressions, pattern-matching against module identifiers, which in Node are represented as absolute file-system paths.
Originally intended as an aid to \sys's development and debugging, this option proved useful enough for writing the three analyses that we decided to expose them to users.
Examples of use include blacklisting built-in libraries or white-listing only the newest-imported library.
% This is useful, for example, when...

@@

Fig.~\ref{fig:ex2} exemplifies \sys's transformation techniques in the context of JavaScript.
\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.

@@

Individual analysis are implemented using a set of templates that provide initial constructs.
%% Individual transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
%% These skeletons provide hooks for end-developers writing analyses.
%% Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
%% These hooks are then extended or rewritten by developers to
\sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
Individual analyses are between 100--200 lines of code, but a significant part of this code is common across analyses.

@@

\begin{verbatim}
let fs = require('fs');
let count = {};
forevery.global.in(/serial/) = {
  pre: (name, path, _) => {
    let id = resolve(name, path);
    count[id] = count[id]?  count[id] + 1 : 1;
  }
};
process.on('exit', () => {
  fs.writeFileSync('acl.json',
                   'utf-8',
                   JSON.stringify(count));
});
\end{verbatim}

@@

\heading{Security Analysis}
To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy that analyzes accesses for every library-to-library combination.
The analysis treats built-in libraries and global variables as modules,
% and generates a list of permissions for each of their fields.
and develops a permission model where individual fields are governed by permission sets containing combinations of read, write, and execute permissions:
 (i) a read permission (\R) indicates that a consumer read a value, including assigning it to a variable and passing it around to other modules;
 (ii) a write permission (\W) indicates that a consumer modified or deleted a value; and
 (iii)  an execute permission (\X) indicates that a consumer to executed a value---\eg a function or a method---or invoked a constructor (usually prefixed by \ttt{new}).

The resulting permission sets are organized as a collection of maps, one per library, each indexed by object-paths such as \ttt{Math.add: RX}.
% that correspond to values of other modules or global-like language names.

\heading{Performance Diagnosis}
To conduct performance diagnosis, we develop a profiling analysis that operates at two levels:
 (i) module-boundary wrappers that collecting profiling statistics for calls between modules by wrapping module interfaces; and
 (ii) an aggregator function that collects statistics from all boundary wrappers and generates a model of library load under the current workload.

Boundary wrappers operate at a higher-frequency intervals than the aggregator, which operates on summaries.
Their analysis focuses on function values (\eg functions, methods, constructors), skipping all other direct field accesses.
Functions are wrapped with prologue and epilogue wrappers that record statistics from the Node.js runtime---for now, a frequency counter and a timer between prologue-to-epilogue invocations.
% Many statistics are available by the Node.js runtime, including memory and garbage-collection statistics, 
Boundary wrappers summarize these statistics by periodically sending a windowed, weighted average of call latencies to the aggregator function.

@@

\heading{Type Invariant Discovery}
To infer type invariants for serialization specifications, we develop a simple type system and use our analysis to map values to types.

The type system is modeled after the simply-typed lambda calculus augmented with:
  (i) unions (sum types), such as \ttt{a | b | c}, 
  (ii) JavaScript-specific types such as \ttt{null}, \ttt{NaN}, or \ttt{undefined}, and
  (iii) a \ttt{native} type for values that cannot be serialized, like \ttt{console.log}.
Support for union types is useful for when our analysis witnesses variables holding values of different types---although, in practice,  programs tend to make calls of the same type across their entire lifetime~\cite{daikon}.

Our implementation also uses a base set of JavaScript types and rules to deconstruct complex types into their elementary building blocks.
% Knowing how to deconstruct a type to its structural primitives allows walking values---
For example, the analysis extracts that an object of type \ttt{user} is comprised of two \ttt{string}s (first and last name) and a \ttt{number} (age).
% To achieve this, the analysis makes use of introspection to identify

@@

\sys's  development achieves goals~\sx{goals}, demonstrating that it is indeed feasible to build a frameworks that 
  operates as a library around an existing runtime,
  does not require learning a new language and tools, and 
  gets meaningful information by operating only at library boundaries, 
% Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
In this section, we report on \sys's performance characteristics:
% At a high level, we are interested in three questions:
  (i) the overheads of the \sys's underlying building blocks;
  (ii) the overhead of different analysis on real libraries, and how this compares with production dynamic analysis frameworks; and
  (iii) an evaluation of \sys's behavior using our analyses on realistic, multi-library applications.
% For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
% For the second question, we use real libraries and compare them with an analysis written in Jalangi~\sx{meso}.
% For the third question, we use a combination of real applications~\sx{macro}.

Several takeaways are worth highlighting.
Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation frameworks.
\sys supports high-performance analysis at the boundaries of individual libraries, adding on average less than \fixme{2$\times$}.
Finally, \sys seems to scale well to large applications with hundreds of libraries while interposing on several thousands of objects.

Experiments were conducted on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
In terms of software, we used Docker version 18.09.7 running a minimal Ubuntu 14.04.6, Jalangi v2, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
All times reported are in \textbf{ms}, averaged over 1K runs;
  \textbf{SA}, \textbf{PD}, and \textbf{TID} respectively stand for security analysis, performance diagnosis, and type-invariant discovery.

@@

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Synthetic Micro-benchmarks}.
		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
    All timings are in $ms$.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
\toprule
	            &   Base    &  SA     & PD      &  TID    \\
\midrule
globals.js    &   0.90    &  4.70   &  4.54   &  4.30   \\
something2    &   1.44    &  6.46   &  6.24   &  5.96   \\
counter.js    &   3.37    &  6.26   &  6.32   &  5.72   \\
something4    &   7.79    &  13.54  &  13.31  &  12.8   \\
delay.js      &   24661   &  24848  &  24754  &  24760  \\
something6    &   4.06    &  7.24   &  7.16   &  6.79   \\
something7    &   4.11    &  7.25   &  7.23   &  6.86   \\
cycles.js     &   4.32    &  8.32   &  8.19   &  7.73   \\
\bottomrule
\end{tabular*}
\label{tab:synthetic}
\vspace{-5mm}
\end{table}

Table~\ref{tab:synthetic} depicts the results of the three analysis applied to a subset of our benchmarks.
Not all analysis-benchmark combinations are useful---\ie some modules do not feature interesting access or performance patterns.
Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
The \ttt{delay.js} is the PD benchmark mentioned earlier, with static bottlenecks.
Initial loading time, affected by transformations altering the environment, is not affected (delta is under 1ms).

To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
  unmodified and proxy-wrapped.
Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
The proxy-wrapped version introduces interposition at every level.
Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.

We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we experienced with real modules).
The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis.

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{\sys-augmented single-library programs}.
    The table shows the overheads of applying the three analyses to the test suites of eight libraries (with Minimist involving five test cases).
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
\toprule
                               & Base   &  SA   & PD     &   TID   \\
\midrule
Classnames~\cite{classnames}   &  2.72  & 6.62  &  6.61  &  6.10   \\
Debug~\cite{debug}             & 31.39  & 33.54 &  33.94 &  33.96  \\
Minimist~\cite{minimist}       &        &       &        &         \\
~~~-t1                         & 31.46  & 60.13 &  60.00 &  56.62  \\
~~~-t2                         & 19.17  & 59.77 &  60.75 &  57.15  \\
~~~-t3                         & 21.64  & 205.2 &  205.53&  132.25 \\
~~~-t4                         & 20.69  & 59.70 &  60.75 &  59.92  \\
~~~-t5                         & 20.49  & 70.48 &  72.20 &  64.71  \\
Moment~\cite{moment}           & 31.73  & 48.04 &  49.23 &  44.95  \\
yargs~\cite{yargs}             & 13.42  & 13.00 &  14.41 &  13.47  \\
chalk~\cite{chalk}             & 17.37  & 24.42 &  26.01 &  26.32  \\
colorette~\cite{colorette}     & 08.10  & 13.85 &  13.41 &  13.16  \\
mkdirp~\cite{mkdirp}           & 116.37 & 1959.52 & 1392.64 & 1252 \\
\bottomrule
\end{tabular*}
\label{tab:meso}
\vspace{-5mm}
\end{table}

@@

\begin{figure*}[t]
  \centering
   \includegraphics[width=0.95\textwidth]{./figs/meso.pdf}
  \caption{
    \textbf{Analysis overheads.}
    The plot compares a series of modules from single-library programs taken from Jalangi between three setups:
		(i) Vanilla JavaScript, (ii) global-use analysis using Jalangi, (iii) global-use analysis using \sys.
    Global-use analysis is a relatively simple analysis that tracks accesses of global variables in the program~\cf{meso}.
  }
  \label{fig:meso}
  \vspace{-3mm}
\end{figure*}

@@

In the first experiment, we collect a diverse set of eight popular libraries from npm, 
% used by thousands of other projects,
on the order of hundreds of lines of code.
As a workload, we use the project-internal test suite that comes bundled with each library (invocable by \ttt{npm test});
  \ttt{minimist} involves several distinct test harnesses, which we 
These tests stress functionality as expected by the authors of the library, and confirms compatibility with all of its functionality.
We apply \sys using the three analyses we developed, and compare the results with their baseline performance (Tab.~\ref{tab:meso}).
The results show that executions augmented with analyses are within 2$\times$, averaging \fixme{XX\%}.
Different benchmarks put a different pressure on \sys's wrappers---some resulting in the invocation of as many as \fixme{XXX} wrappers, as shown by the resulting analysis output on disk.

In the second experiment, we apply \sys on Jalangi2's extensive test suite (Fig.~\ref{fig:meso}) and compare \sys's performance to that of Jalangi2.
To be fair in our comparison, we design a simple analysis from scratch that both frameworks can support---namely, one for tracking counts of global variable accesses~\sx{impl2}.
The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
  the effort of employing \sys as a library was significantly lower than Jalangi2, for which we \fixme{relied} on a Docker container to simplify the framework's setup.
The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
We note here that Jalangi2 has a runtime performance that is significantly faster than the classic Jalangi, as it eschews record/replay capabilities.
Jalangi2 is more powerful, expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.

@@

Program dialysis depends on a few features provided by the programming language.
In this section, we start by describing its requirements~\sx{reqs} and then reflect on some of its strengths and weaknesses~\sx{principles}.

>>>>

\usepackage{soul}
\usepackage{xspace}
\usepackage{color}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{alltt}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{listings}

\lstdefinelanguage{js}{
  morekeywords={typeof, let, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  keywordstyle=\color{purple}\ttfamily,
  keywordstyle=[3]\color{orange},
  keywords=[3]{SBX, PROC},
  ndkeywords={class, export, require, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{cyan}\ttfamily, %bfseries
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  commentstyle=\color{lightgray},
% morecomment=[s]{/\\*\\*, \\*/},
  stringstyle=\color{blue}\ttfamily,
  basicstyle=\footnotesize\ttfamily,  % the size of the fonts that are used for the code
  numberstyle=\tiny\color{gray},   % the style that is used for the line-numbers
  morestring=[b]',
  morestring=[b]",
% moredelim=[s][\color{gray}]{c:}{>},
% moredelim=[s][\color{orange}]{/*}{/}
}

\lstdefinelanguage{es}{
  morekeywords={string, number, bool, p, v, e, x},
  keywordstyle=\color{darkgray},
  keywordstyle=[3]\color{orange},
  keywords=[3]{SBX, PROC},
  ndkeywords={undefined, null, delete},
  ndkeywordstyle=\color{black}\ttfamily\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  commentstyle=\color{lightgray},
% morecomment=[s]{/\\*\\*, \\*/},
  stringstyle=\color{darkgray}\ttfamily,
  morestring=[b]',
  morestring=[b]",
% numbersep=1pt,
% numberstyle=\footnotesize\bf\color{gray},   % the style that is used for the line-numbers
  abovecaptionskip=0em,
  aboveskip=0em,
  belowcaptionskip=0em,
  belowskip=0em,
  frame=none,                     % adds a frame around the code
% moredelim=[s][\color{gray}]{c:}{>},
% moredelim=[s][\color{orange}]{/*}{/}
}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\small\ttfamily,  % the size of the fonts that are used for the code
  upquote=true,
  captionpos=b,                    % sets the caption-position to bottom
% frame=B,                    % adds a frame around the code
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=3pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{gray},   % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
}

@@

This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top Node.js v8.9.4~\sx{impl1}, and 
% We start with the internals of \sys's implementation, and then describe
including the three analyses developed atop \sys~\sx{impl2}.
Discussion of how other environments diverge from JavaScript is left for the next section~\sx{reqs}.

The aforementioned dialysis design can be implemented in either of two ways.
The first is to implement \sys as a modified version of the runtime, in which several stages of its library-loading facility have been augmented in-place. % with the techniques described earlier.
The second approach is to implement \sys as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.
% 
With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of Node's module system.
We went with the second approach, as looser coupling seems to have several benefits:
  it does not require \sys's users to have a second Node copy only for running analyses;
  it removes \sys's developers from the critical path of updates between the Node developers and its users; 
  and it simplifies \sys's comparison with vanilla Node (both in terms of performance and correctness).
The primary drawback was missing a few opportunities for lowering runtime-performance and development-effort.

% It sketches the Node runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.

@@

Node's module system is implemented entirely in JavaScript, exposing a library-local \ttt{require} function for importing modules.
Loading a fresh module % with \ttt{require("foo")}
  corresponds to the following five stages, all of which are augmented by \sys:
(R) Resolution: identify the file to which the module specified corresponds, locate it in the file-system, and assign its absolute path as a module identifier.
(L) Loading: depending on the file type, identify the corresponding loader---\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc
% Identifiers are absolute paths.
(W) Wrapping: wrap the module so that local names do not escape the module's scope and Node's module-local names get resolved.
(E) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
(C) Caching: add the module to a handful of module-related caches, for purposes of consistency and performance.

% The resolution algorithm is somewhat convoluted, because it depends on several different facts (including the type of the file requested, whether it is a globally installed, whether it is a directory \etc).
% It does not require any \sys support beyond copying the directory that contains the source code of the all the modules onto the remote host.
\sys interposes on all of these steps to facilitate transformations.
Interposing on resolution (R) makes the module identifier available to \sys without affecting the (incredibly convoluted!) module resolution algorithm.
If the module's type is one \sys can analyze, it fetches the corresponding analysis during loading (L).
Wrapping (W) and evaluation (E) are where \sys transforms the module boundary.
\sys replaces Node's wrapper function to pass an additional argument, the modified context \ttt{CTX}.
\sys comes with a hard-coded list of names corresponding to the specific version of EcmaScript and Node.
Identifying names coming from EcmaScript was relatively easy, as the standard makes them explicit.
Node's global names are described at various parts of the documentation, but library-local names required close inspection of Node's internals; fortunately, these were only five names.

@@

% \begin{lstlisting}
% let lib = `
%  function (exports, require, module,
%            __filename, __dirname, CTX) {
%    let Math = CTX.Math
%    let console = CTX.console
%    //...[more definitions]
%    ${moduleSource}
%  });`;
% \end{lstlisting}

We found it useful to add an option for white- and black-listing libraries.
The configuration object accepts \ttt{only} and \ttt{not} expressions that indicate whether a module identifier will be part of the analysis.
These expressions contain sets of regular expressions, pattern-matching against module identifiers, which in Node are represented as absolute file-system paths.
Originally intended as an aid to \sys's development and debugging, this option proved useful enough for writing the three analyses that we decided to expose it to \sys's users.
Examples of its use include blacklisting built-in libraries or white-listing only the library imported most recently.
% This is useful, for example, when...

@@

Fig.~\ref{fig:ex2} exemplifies \sys's transformation techniques in the context of JavaScript.
\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers, creates a modified version of the surrounding context, and binds it to the library.

@@

Individual analysis are implemented using a set of templates that provide initial constructs.
%% Individual transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
%% These skeletons provide hooks for end-developers writing analyses.
%% Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
%% These hooks are then extended or rewritten by developers to
\sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
Individual analyses are about 60 lines of code, but a significant part of this code is common across them.

@@

\begin{lstlisting}
let fs = require("fs");
let count = {};
forevery.global.in(/serial/) = {
  pre: (name, path, _) => {
    let id = resolve(name, path);
    count[id] = count[id]?  count[id] + 1 : 1;
  }
};
process.on("exit", () => {
  fs.writeFileSync("acl.json",
                   "utf-8",
                   JSON.stringify(count));
});
\end{lstlisting}

@@

\heading{Security Analysis}
To address the security concerns of third-party libraries, we developed a concrete \ttt{RWX} policy that analyzes accesses for every library-to-library combination.
The analysis treats built-in libraries and global variables as modules,
% and generates a list of permissions for each of their fields.
and develops a permission model where individual fields are governed by permission sets containing combinations of read, write, and execute permissions:
 (i) a read permission (\R) indicates that a consumer read a value, including assigning it to a variable and passing it around to other modules;
 (ii) a write permission (\W) indicates that a consumer modified or deleted a value; and
 (iii)  an execute permission (\X) indicates that a consumer executed a value---\eg a function or a method---or invoked a constructor (usually prefixed by \ttt{new}).

The resulting permission sets are organized as collections of maps, one per library, indexed by object-paths---\eg \ttt{Math.add: RX}.
% that correspond to values of other modules or global-like language names.

\heading{Performance Diagnosis}
We develop a profiling analysis that operates at two levels:
 (i) module-boundary wrappers that collect profiling statistics for calls between modules by wrapping module interfaces; and
 (ii) an aggregator function that collects statistics from all boundary wrappers and generates a model of library load under the current workload.

Boundary wrappers operate at a higher-frequency intervals than the aggregator, which operates on summaries.
Their analysis focuses on function calls, skipping all other direct field accesses.
Functions are wrapped with prologue and epilogue wrappers that record statistics from the Node.js runtime---for now, a frequency counter and a timer between prologue-to-epilogue invocations.
% Many statistics are available by the Node.js runtime, including memory and garbage-collection statistics, 
Boundary wrappers summarize these statistics by periodically sending a windowed, weighted average of call latencies to the aggregator function.

@@

\heading{Type Invariant Discovery}
To infer type invariants for serialization specifications, we base our analysis on a simple type system modeled after the simply-typed lambda calculus augmented with:
  (i) unions (sum types), such as \ttt{a | b | c}, 
  (ii) JavaScript-specific types such as \ttt{null}, \ttt{NaN}, or \ttt{undefined}, and
  (iii) a \ttt{native} type for values that cannot be serialized, such as \ttt{console.log}.
Support for union types is useful for when our analysis witnesses variables holding values of different types---although, in practice,  programs tend to make calls of the same type across their entire lifetime~\cite{daikon}.

Our implementation also uses a base set of JavaScript types and rules to deconstruct complex types into their elementary building blocks.
% Knowing how to deconstruct a type to its structural primitives allows walking values---
For example, it unpacks a type \ttt{user} into two \ttt{string}s (first and last name) and a \ttt{number} (age).
% To achieve this, the analysis makes use of introspection to identify

@@

\sys's  development achieves goals \textbf{G1--3}~\sx{goals}, demonstrating that it is indeed feasible to build a framework that 
  operates as a library around an existing runtime,
  does not require learning a new language, and 
  gets meaningful information while operating only at library boundaries.
% Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
In this section, we report on \sys's performance characteristics:
% At a high level, we are interested in three questions:
  (i) the overheads of its underlying building blocks;
  (ii) dialysis on real libraries, and how they compare to a production-grade dynamic analysis; and
  (iii) \sys's behavior on realistic  multi-library applications.
% For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
% For the second question, we use real libraries and compare them with an analysis written in Jalangi~\sx{meso}.
% For the third question, we use a combination of real applications~\sx{macro}.

Several takeaways are worth highlighting.
Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation frameworks.
\sys's library-level analysis adds a small overhead, less than $2\times$ for the vast majority of libraries and often less than $5ms$.
Finally, \sys scales to large applications with hundreds of libraries while interposing on several thousands of objects.

Experiments were conducted on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
In terms of software, we used Docker version 18.09.7 running a minimal Ubuntu 14.04.6, Jalangi v2, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
All times reported are in \textbf{ms}, averaged over 1K runs;
  \textbf{SA}, \textbf{PD}, and \textbf{TID} respectively stand for security analysis, performance diagnosis, and type invariant discovery.

@@

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Synthetic Micro-benchmarks}.
		Applying the three analyses on a series of synthetic micro-benchmarks, created to stress different features.
    All timings are in $ms$.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
\toprule
	               &   Base    &  SA     & PD      &  TID    \\
\midrule
globals vars     &   0.90    &  4.70   &  4.54   &  4.30   \\
built-in fields  &   1.44    &  6.46   &  6.24   &  5.96   \\
counter          &   3.37    &  6.26   &  6.32   &  5.72   \\
all names        &   7.79    &  13.54  &  13.31  &  12.8   \\
custom delays    &   24661   &  24848  &  24754  &  24760  \\
direct-access    &   4.06    &  7.24   &  7.16   &  6.79   \\
timple-types     &   4.11    &  7.25   &  7.23   &  6.86   \\
cycles           &   4.32    &  8.32   &  8.19   &  7.73   \\
\bottomrule
\end{tabular*}
\label{tab:synthetic}
\vspace{-5mm}
\end{table}

Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of our benchmarks.
The first column indicates the focus of the benchmark; not all analysis-benchmark combinations are useful.
% Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
For example, the ``custom-delay'' benchmark, described earlier, features static bottlenecks across its dependency tree but does not involve interesting access patterns.
The use of \sys adds an overhead that is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
Close inspection confirms that overheads are proportional to the number of wrapped objects and the frequency of accesses:
  most of these benchmarks feature artificially tight loops with high-frequency accesses.
Transformation overheads themselves (not shown in Tab.~\ref{tab:synthetic}) remain under $1ms$.
% is not affected significantly % by transformations altering a library's context

To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
  unmodified and proxy-wrapped.
Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
The proxy-wrapped version introduces interposition at every level.
Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.
% 
We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we saw with real modules).
The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis;
  what is likely to be the overhead is the analysis itself---\eg updating a global aggregator or invoking system-calls to extract timing.

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{\sys-augmented single-library programs}.
    The table shows the overheads of applying the three analyses to the test suites of eight libraries. % (with Minimist involving five test cases).
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
\toprule
                               & Base   &  SA   & PD     &   TID   \\
\midrule
Classnames~\cite{classnames}   &  2.72  & 6.62  &  6.61  &  6.10   \\
Debug~\cite{debug}             & 31.39  & 33.54 &  33.94 &  33.96  \\
Minimist~\cite{minimist}       &        &       &        &         \\
~~~-t1                         & 31.46  & 60.13 &  60.00 &  56.62  \\
~~~-t2                         & 19.17  & 59.77 &  60.75 &  57.15  \\
~~~-t3                         & 21.64  & 205.2 &  205.53&  132.25 \\
~~~-t4                         & 20.69  & 59.70 &  60.75 &  59.92  \\
~~~-t5                         & 20.49  & 70.48 &  72.20 &  64.71  \\
Moment~\cite{moment}           & 31.73  & 48.04 &  49.23 &  44.95  \\
yargs~\cite{yargs}             & 13.42  & 13.00 &  14.41 &  13.47  \\
chalk~\cite{chalk}             & 17.37  & 24.42 &  26.01 &  26.32  \\
colorette~\cite{colorette}     & 08.10  & 13.85 &  13.41 &  13.16  \\
mkdirp~\cite{mkdirp}           & 116.37 & 1959.52 & 1392.64 & 1252 \\
\bottomrule
\end{tabular*}
\label{tab:meso}
\vspace{-5mm}
\end{table}

@@

\begin{figure*}[t]
  \centering
   \includegraphics[width=0.95\textwidth]{./figs/meso.pdf}
  \caption{
    \textbf{Analysis overheads.}
    The plot compares single-library programs taken from Jalangi2 between three setups:
		(i) Vanilla JavaScript, (ii) global-use analysis with Jalangi2, (iii) global-use analysis with \sys.
    Global-use analysis is a simple analysis that tracks accesses of global variables in the program~\cf{meso}.
  }
  \label{fig:meso}
  \vspace{-3mm}
\end{figure*}

@@

In the first experiment, we collect a diverse set of eight popular libraries from npm, 
% used by thousands of other projects,
on the order of hundreds of lines of code.
As a workload, we use each library's internal test suite, with \ttt{minimist} includes several distinct test harnesses.
These tests stress functionality as expected by the library's authors and confirm that \sys does not break it.
We apply \sys using the three analyses we developed, and compare the results with their baseline performance (Tab.~\ref{tab:meso}).
The results show that executions augmented with analyses are within 2--3$\times$, averaging a 80\% slowdown for the largest libraries.
Different benchmarks put a different pressure on \sys's wrappers---some resulting in the invocation of as many as 257 wrappers. % (shown by the analysis output).

In the second experiment, we apply \sys on Jalangi2's extensive test suite (Fig.~\ref{fig:meso}) and compare \sys's performance to that of Jalangi2.
We note that Jalangi2 improves significantly over Jalangi's performance~\cite{jalangi}, as it eschews record/replay capabilities.
To be fair in our comparison, we design a simple analysis from scratch that both frameworks can express---namely, one for tracking counts of global variable accesses~\sx{impl2}.
The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
  the effort of employing \sys as a library was significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
Jalangi2 is more powerful than \sys, capable of expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.

@@

In this section, we start by reflecting on the requirements of dialysis from the programming language~\sx{reqs} and then on some of its strengths and weaknesses~\sx{principles}.
% Program dialysis depends on a few features provided by the programming language.
